\editone{Stellar convective penetration: parameterized theory and dynamical simulations}

### 2021-10-06 manuscript/ms.tex
adds line numbers per apj request
rough draft of response to referee report 1

% Preamble
\documentclass[twocolumn]{aastex631}
\usepackage{natbib}
\usepackage{latexsym}
\usepackage{graphicx}
\usepackage{epsfig}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{epstopdf}
\usepackage{hyperref}

@@

@@

%%%% Title and Abstract
\title{Convective penetration: It exists and we found it}
\author[0000-0002-3433-4733]{Evan H. Anders}
\affiliation{CIERA, Northwestern University, Evanston IL 60201, USA}
\author[0000-0001-5048-9973]{Adam S. Jermyn}
\affiliation{Center for Computational Astrophysics, Flatiron Institute, New York, NY 10010, USA}
\author[0000-0002-7635-9728]{Daniel Lecoanet}
\affiliation{CIERA, Northwestern University, Evanston IL 60201, USA}
\affiliation{Department of Engineering Sciences and Applied Mathematics, Northwestern University, Evanston IL 60208, USA}
\author[0000-0001-8935-219X]{Benjamin P. Brown}
\affiliation{Department Astrophysical and Planetary Sciences \& LASP, University of Colorado, Boulder, CO 80309, USA}

@@

Convective penetration is the process by which convective motions extend beyond the Schwarzschild-stable boundary and mix the entropy gradient to be nearly adiabatic.
\begin{quote}
\emph{
In this paper, we present simulations which exhibit convective penetration.
}
\end{quote}
This process is phenomenologically described in Sec.~\ref{sec:central_results}.

@@

We further explore the simulation from Fig.~\ref{fig:vertical_dynamics_panels} in Fig.~\ref{fig:grad_profiles} by displaying time- and horizontally-averaged 1D profiles of the temperature gradient $\justgrad$ (defined in Sec.~\ref{sec:theory}).
The adiabatic gradient $\gradad$ (purple) has a constant value in the simulation.
Also shown is the radiative gradient $\gradrad$ (orange).
The domain exhibits a classical Schwarzshild-unstable convection zone (CZ) for $z \lesssim 1.04$ where $\gradrad > \gradad$; the upper boundary of this region is denoted by a dashed vertical line.
Above this point, $\gradrad < \gradad$ and the domain would be considered stable by the Schwarzschild criterion.
However, the evolved convective dynamics in Fig.~\ref{fig:vertical_dynamics_panels} have raised $\justgrad \rightarrow \gradad$ in an extended penetration zone (PZ) which extends from $1.04 \lesssim z \lesssim 1.4$.
Above the PZ, $\justgrad$ departs from $\gradad$, returning to $\gradrad$ in a classical stable radiative zone (RZ).

@@

\begin{figure}[t]
\centering
\includegraphics[width=\columnwidth]{grad_profiles.pdf}
\caption{
Horizontally- and temporally-averaged profiles of the thermodynamic gradients from the simulation in Fig.~\ref{fig:vertical_dynamics_panels}.
We plot $\justgrad$ (green) compared to $\gradad$ (purple, a constant) and $\gradrad$ (orange); note the extended penetration zone (PZ) where $\justgrad \approx \gradad > \gradrad$.
\label{fig:grad_profiles}
}
\end{figure}

\section{Theory}
\label{sec:theory}
In this section we derive a theoretical model of convective penetration by examining the energetics and energy fluxes in the Schwarzschild-unstable convection zone (CZ) and penetration zone (PZ).
In Sec.~\ref{sec:theory_equations}, we describe our equations and problem setup and define the heat fluxes.
In Sec.~\ref{sec:theory_energy}, we build a parameterized theory based on the kinetic energy (KE) equation.
We find that imbalances in KE source terms within the CZ determine the extent of the PZ.
%We find that excess KE in the convection zone can cause a penetration zone to form.
By balancing the excess KE generation in the CZ with buoyancy-braking and dissipation work terms in the PZ, we are able to derive the size of the PZ.
We find that a description of the size of a theoretical PZ does not depend on the often-considered stiffness, which measures the relative stability between the convection zone and an adjacent radiative zone.

\subsection{Equations \& flux definitions}
\label{sec:theory_equations}
Throughout this work, we will utilize a modified version of the incompressible Boussinesq equations,
\begin{align}
&\grad\dot\vec{u} = 0 
\label{eqn:incompressible} \\
&\partial_t \vec{u} + \vec{u}\dot\grad\vec{u} = -\frac{1}{\rho_0}\grad p + \frac{\rho_1}{\rho_0}\vec{g} + \nu\grad^2 \vec{u} 
\label{eqn:momentum} \\
&\partial_t T + \vec{u}\dot\grad T + w \gradad + \grad\dot[-k \grad \overline{T}] = \chi\grad^2 T' + Q
\label{eqn:temperature} \\
&\frac{\rho_1}{\rho_0} = -|\alpha| T.
\label{eqn:boussinesq}
\end{align}
Here, the density is decomposed into a uniform, constant background $\rho_0$ with fluctuations $\rho_1$ which appear only in the buoyancy force and depend on the temperature $T$ and the coefficient of thermal expansion $\alpha = \partial\ln\rho / \partial T$.
We define the velocity vector $\vec{u}$, the viscous diffusivity $\nu$, the thermal diffusivity $\chi$, the bulk internal heating $Q$, the adiabatic gradient $\gradad$, and a height-dependent thermal conductivity $k$.
We will consider Cartesian coordinates $(x, y, z)$ with a constant vertical gravity $\vec{g} = -g\hat{z}$.
Throughout this work, we will represent horizontal averages with bars ($\overline{\,\cdot\,}$) and fluctuations away from those averages with primes ($'$).
Thus, in Eqn.~\ref{eqn:temperature}, $\bar{T}$ is the horizontally averaged temperature and $T'$ are fluctuations away from that; both of these fields evolve in time according to Eqn.~\ref{eqn:temperature}.

@@

\begin{figure}[t!]
\centering
\includegraphics[width=\columnwidth]{theory_profiles.pdf}
\caption{
Temporally- and horizontally-averaged profiles from Eqn.~\ref{eqn:kinetic_energy_1D} in the simulation in Fig.~\ref{fig:vertical_dynamics_panels}.
The vertical dashed line denotes the Schwarzschild CZ boundary, and the vertical solid line corresponds to the top of the PZ.
(upper) Kinetic energy fluxes $\bar{\mathcal{F}}$, which go to zero at the bottom boundary and the top of the PZ.
(bottom) Source terms from Eqn.~\ref{eqn:kinetic_energy_1D} normalized by the maximum of $\overline{\mathcal{B}}$ ($\bar{\mathcal{F}}$ in the upper panel is similarly normalized).
The buoyancy source $\bar{\mathcal{B}}$ changes sign at the Schwarzschild boundary, and $\bar{\Phi}$ is positive-definite.
\label{fig:theory_profiles}
}
\end{figure}

Taking a dot product of the velocity and Eqn.~\ref{eqn:momentum} reveals the kinetic energy equation,
\begin{equation}
\frac{\partial \mathcal{K}}{\partial t}
+ \grad\dot\mathcal{F}
= \mathcal{B} - \Phi,
%\frac{\partial}{\partial t}\left(\frac{|\vec{u}|^2}{2}\right) 
%+ \grad\dot\left[\vec{u}\left(\frac{|\vec{u}|^2}{2} + \frac{p}{\rho_0}\right) - \nu\vec{u}\cross\vec{\omega}\right]
%= |\alpha| g w T - \nu|\vec{\omega}|^2,
\label{eqn:kinetic_energy}
\end{equation}
where we define the kinetic energy $\mathcal{K} \equiv |\vec{u}|^2/2$, the fluxes of kinetic energy $\mathcal{F} \equiv \left[\vec{u}(\mathcal{K} + p/\rho_0) - \nu\vec{u}\cross\vec{\omega} \right]$, the buoyant energy generation rate $\mathcal{B} \equiv |\alpha| g w T'$, and the viscous dissipation rate $\Phi \equiv \nu |\vec{\omega}|^2$ where $\vec{\omega} = \grad\cross\vec{u}$ is the vorticity and $|\vec{u}|^2 = \vec{u}\dot\vec{u}$ \& $|\vec{\omega}|^2 = \vec{\omega}\dot\vec{\omega}$.
We next take a horizontal- and time-average of Eqn.~\ref{eqn:kinetic_energy} (we absorb the time-average into the horizontal-average $\bar{\,\cdot\,}$ notation for simplicity).
Assuming that $\bar{\mathcal{K}}$ reaches a statistically stationary state, convective motions satisfy
\begin{equation}
\frac{d\bar{\mathcal{F}}}{dz} = \bar{\mathcal{B}} - \bar{\Phi}.
\label{eqn:kinetic_energy_1D}
\end{equation}
Each profile in Eqn.~\ref{eqn:kinetic_energy_1D} is shown in Fig.~\ref{fig:theory_profiles} for the simulation whose dynamics are displayed in Fig.~\ref{fig:vertical_dynamics_panels}.
As in Fig.~\ref{fig:grad_profiles}, the Schwarzschild CZ boundary is plotted as a dashed line, and the top of the PZ is plotted as a solid vertical line.
In the top panel, we display $\bar{\mathcal{F}}$, neglecting the viscous flux term which is only nonzero in a small region above the bottom boundary.
We see that $\bar{\mathcal{F}}$ is zero at the bottom boundary (left edge of plot) and at the top of the PZ.
In the bottom panel, we plot $\bar{\mathcal{B}}$ and $\bar{\Phi}$; we see that $\bar{\mathcal{B}}$ changes sign at the Schwarzschild CZ boundary, and that $\bar{\Phi}$ is positive-definite.

At the boundaries of the convecting region, $\bar{\mathcal{F}}$ is zero (Fig.~\ref{fig:theory_profiles}, upper panel).
We integrate Eqn.~\ref{eqn:kinetic_energy_1D} vertically between these zeros to find
\begin{equation}
\int \bar{\mathcal{B}}\,dz = \int \bar{\Phi}\,dz.
\label{eqn:integral_constraint}
\end{equation}
Integral constraints of this form are the basis for a broad range of analyses in Boussinesq convection \citep[see e.g.,][]{ahlers_etal_2009, goluskin2016} and were considered in the context of penetrative stellar convection by \citet{roxburgh1989}.
Eqn.~\ref{eqn:integral_constraint} is the straightforward statement that work by buoyancy on large scales must be balanced by viscous dissipation on small scales.

We break up the convecting region into a Schwarzschild-unstable ``convection zone'' (CZ) and an extended ``penetration zone'' (PZ); we assume that convective motions efficiently mix $\justgrad \rightarrow \gradad$ in both the CZ and PZ.
The buoyant energy generation is proportional to the convective flux, $\bar{\mathcal{B}} = |\alpha|g\bar{w T'} = |\alpha| g \bar{\Fconv}$, and is positive in the CZ and negative in the PZ (see Fig.~\ref{fig:theory_profiles}, bottom panel).
Breaking up Eqn.~\ref{eqn:integral_constraint}, we see that
\begin{equation}
%\int_{\rm{CZ}} \bar{\mathcal{B}}\,dz \qquad=\qquad
\int_{\rm{CZ}} \bar{\mathcal{B}}\,dz \,\,=\,\,
\int_{\rm{CZ}} \bar{\Phi}\,dz + \int_{\rm{PZ}} \bar{\Phi}\,dz + \int_{\rm{PZ}}(-\bar{\mathcal{B}})\,dz.
\label{eqn:constraint_cz_pz_split}
\end{equation}
Eqn.~\ref{eqn:constraint_cz_pz_split} is arranged so that the (positive) buoyant engine of convection is on the left-hand side, and the (positive) sinks of work are on the RHS.
If viscous dissipation in the CZ does not balance the buoyant generation of energy in the CZ, the kinetic energy of the convective flows grows, resulting in a penetrative region.
This region grows with time until Eqn.~\ref{eqn:constraint_cz_pz_split} is satisfied.
We see that the viscous dissipation and buoyancy breaking felt by flows in the PZ determine its size.
We now define
\begin{equation}
f \equiv \frac{\int_{\rm{CZ}} \bar{\Phi}\,dz}{\int_{\rm{CZ}}\bar{\mathcal{B}}\,dz},
\label{eqn:f_defn}
\end{equation}
the measurable fraction of the buoyant engine consumed by CZ dissipation.
Eqn.~\ref{eqn:constraint_cz_pz_split} can then be rewritten as
\begin{equation}
\frac{\int_{\rm{PZ}}(-\bar{\mathcal{B}})\,dz}{\int_{\rm{CZ}} \bar{\mathcal{B}}\,dz}
+ \frac{\int_{\rm{PZ}} \bar{\Phi}\,dz }{\int_{\rm{CZ}} \bar{\mathcal{B}}\,dz}
= (1 - f).
\label{eqn:first_pz_parameterization}
\end{equation}
We will measure and report the values of $f$ achieved in our simulations in this work.
Eqn.~\ref{eqn:first_pz_parameterization} provides two limits on a hypothetical PZ:
\begin{enumerate}
\item In the limit that $f \rightarrow 0$, viscous dissipation is inefficient.
Reasonably if we also assume that $\int_{\rm{PZ}}\bar{\Phi}\,dz \rightarrow 0$, Eqn.~\ref{eqn:first_pz_parameterization} states that the PZ must be so large that its negative buoyant work is equal in magnitude to the positive buoyant work of the CZ.
This is the integral constraint on the maximum size of the PZ that \citet{roxburgh1989} derived.
\item In the limit that $f \rightarrow 1$, viscous dissipation efficiently counteracts the buoyancy work in the CZ.
Per Eqn.~\ref{eqn:first_pz_parameterization}, the positive-definite PZ terms must approach zero and no PZ develops in this limit.
This is mathematically equivalent to standard boundary-driven convection experiments.
\end{enumerate}
In general, we anticipate from the results of e.g., \citet{currie_browning_2017} that $f$ is closer to 1 than 0, but its precise value must be measured from simulations.
Indeed, we find that $f \gg 0$ but $f < 1$ in our simulations (see e.g., Fig.~\ref{fig:theory_profiles}, bottom panel\footnote{the bulk dynamics suggest by eye $f \sim 0.5$, but due to e.g., the height dependence of $\bar{\mathcal{B}}$ in our simulations we measure $f \approx 0.74$.}).
Our simulations produce typical values of $f \sim 0.7$.

Assuming that a PZ of height $\delp$ develops above a CZ of depth $L_{\rm{CZ}}$, we model the PZ dissipation as
\begin{equation}
\int_{\rm{PZ}} \bar{\Phi}\,dz = \xi\frac{\delp}{L_{\rm{CZ}}}\int_{\rm{CZ}}\bar{\Phi}\,dz = \xi \delp \Phi_{\rm{CZ}}.
\label{eqn:xi_defn}
\end{equation}
Here $\Phi_{\rm{CZ}}$ is the volume-averaged dissipation rate in the CZ and $\xi$ is a measurable parameter in ${[0, 1]}$ that describes the shape of the dissipation profile as a function of height in the PZ.
In words, we assume that $\bar{\Phi}(z = L_s) \approx \Phi_{\rm{CZ}}$ at the CZ-PZ boundary and that $\bar{\Phi}$ decreases with height in the PZ.
The shape of $\bar{\Phi}$ determines $\xi$; a linear falloff gives $\xi = 1/2$, a quadratic falloff gives $\xi = 2/3$, and $\xi = 1$ assumes no falloff.
With this parameterization, and $\bar{\mathcal{B}} \propto \bar{\Fconv}$, we rewrite Eqn.~\ref{eqn:first_pz_parameterization},
\begin{equation}
-\frac{\int_{\rm{PZ}}\bar{\Fconv}\,dz}{\int_{\rm{CZ}}\bar{\Fconv}\,dz} + f\xi\frac{\delp}{L_{\rm{CZ}}}
= (1 - f).
\label{eqn:theory_fraction}
\end{equation}
The fundamental result of this theory is Eqn.~\ref{eqn:theory_fraction}, which is a parameterized and generalized form of \citet{roxburgh1989}'s integral constraint.
This equation is also reminiscent of \citet{zahn1991}'s theory, and says that the size of a PZ is set by the profile of $\gradrad$ near the convective boundary.
A parameterization like Eqn.~\ref{eqn:theory_fraction} can be implemented in stellar structure codes and used to find the extent of penetration zones under the specification of $f$ and $\xi$.
The parameters $f$ and $\xi$ are measurables which can be constrained by direct numerical simulations, and we will measure their values in this work.
In general, we expect that $f$ and $\xi$ should not change too drastically with other simulation parameters.

In order to derive a specific prediction for the PZ height, one must specify the vertical shape of $\overline{\Fconv}$.
We will study two cases in this work, laid out below.
In both of these cases, we define a nondimensional ``Penetration Parameter'' whose magnitude is set by the ratio of the convective flux slightly above and below the Schwarzschild convective boundary $L_s$ (assuming $\justgrad = \gradad$ in the CZ and PZ),
\begin{equation}
%\mP \equiv -\frac{\overline{\Fconv}(z = L_s - \epsilon)}{\overline{\Fconv}(z = L_s + \epsilon)}
\mP \equiv -\frac{\bar{\Fconv}_{\rm{CZ}}}{\bar{\Fconv}_{\rm{PZ}}}.
\label{eqn:theory_P_defn}
\end{equation}
Since $\Fconv < 0$ in the PZ, the sign of $\mP$ is positive.
Intuitively, $\mP$ describes which terms are important in Eqn.~\ref{eqn:first_pz_parameterization}.
When $\mP \ll 1$, the buoyancy term dominates in the PZ and dissipation can be neglected there.
When $\mP \gg 1$, buoyancy is negligible and dissipation constrains the size of the PZ.
When $\mP \sim 1$, both terms matter.

>>>>

% Preamble
\documentclass[twocolumn, linenumbers]{aastex631}
\usepackage{natbib}
\usepackage{latexsym}
\usepackage{graphicx}
\usepackage{epsfig}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{epstopdf}
\usepackage{hyperref}
\usepackage{xcolor}

@@

\newcommand{\editone}[1]{\textcolor{orange}{#1}}

@@

%%%% Title and Abstract
\title{\editone{Stellar convective penetration: parameterized theory and dynamical simulations}}
\author[0000-0002-3433-4733]{Evan H. Anders}
\affiliation{CIERA, Northwestern University, Evanston IL 60201, USA}
\author[0000-0001-5048-9973]{Adam S. Jermyn}
\affiliation{Center for Computational Astrophysics, Flatiron Institute, New York, NY 10010, USA}
\author[0000-0002-7635-9728]{Daniel Lecoanet}
\affiliation{CIERA, Northwestern University, Evanston IL 60201, USA}
\affiliation{Department of Engineering Sciences and Applied Mathematics, Northwestern University, Evanston IL 60208, USA}
\author[0000-0001-8935-219X]{Benjamin P. Brown}
\affiliation{Department Astrophysical and Planetary Sciences \& LASP, University of Colorado, Boulder, CO 80309, USA}

@@

Convective penetration is the process by which convective motions extend beyond the Schwarzschild-stable boundary and mix the entropy gradient to be nearly adiabatic.
\begin{quote}
\emph{
    In this paper, we present simulations which exhibit convective penetration.
}
\end{quote}
This process is phenomenologically described in Sec.~\ref{sec:central_results}.
\editone{
    In this work, the convection zone lies beneath an adjacent stable layer and convection penetrates upwards; our results equally apply to the reversed problem.
}

@@

We further explore the simulation from Fig.~\ref{fig:vertical_dynamics_panels} in Fig.~\ref{fig:grad_profiles} by displaying time- and horizontally-averaged 1D profiles of the temperature gradient $\justgrad$ (defined in Sec.~\ref{sec:theory}).
The adiabatic gradient $\gradad$ (purple) has a constant value in the simulation.
Also shown is the radiative gradient $\gradrad$ (orange).
The domain exhibits a classical Schwarzshild-unstable convection zone (CZ) for $z \lesssim 1.04$ where $\gradrad > \gradad$; the upper boundary of this region is denoted by a dashed vertical line.
Above this point, $\gradrad < \gradad$ and the domain would be considered stable by the Schwarzschild criterion.
However, the evolved convective dynamics in Fig.~\ref{fig:vertical_dynamics_panels} have raised $\justgrad \rightarrow \gradad$ in an extended penetration zone (PZ) which extends from $1.04 \lesssim z \lesssim 1.3$.
\editone{
    At the top of the PZ, between $1.3 \lesssim z \lesssim 1.4$, there is a ``thermal adjustment layer'' where convective motions give way to conductive transport and $\justgrad$ adjusts from $\gradad$ to $\gradrad$.
    Above $z \gtrsim 1.4$, $\justgrad \approx \gradrad$ in a classical stable radiative zone (RZ).
}

@@

\begin{figure}[t]
\centering
\includegraphics[width=\columnwidth]{grad_profiles.pdf}
\caption{
Horizontally- and temporally-averaged profiles of the thermodynamic gradients from the simulation in Fig.~\ref{fig:vertical_dynamics_panels}.
We plot $\justgrad$ (green) compared to $\gradad$ (purple, a constant) and $\gradrad$ (orange); note the extended penetration zone (PZ) where $\justgrad \approx \gradad > \gradrad$.
    \editone{
        The dashed vertical line denotes the Schwarzschild boundary of the convection zone (CZ), the greyed region denotes the thermal adjustment layer, and the solid vertical line denotes the bottom of the radiative zone (RZ).
    }
\label{fig:grad_profiles}
}
\end{figure}

\section{Theory}
\label{sec:theory}
In this section we derive a theoretical model of convective penetration by examining the energetics and energy fluxes in the Schwarzschild-unstable convection zone (CZ) and penetration zone (PZ).
In Sec.~\ref{sec:theory_equations}, we describe our equations and problem setup and define the heat fluxes.
In Sec.~\ref{sec:theory_energy}, we build a parameterized theory based on the kinetic energy (KE) equation.
We find that imbalances in KE source terms within the CZ determine the extent of the PZ.
%We find that excess KE in the convection zone can cause a penetration zone to form.
By balancing the excess KE generation in the CZ with \editone{buoyant deceleration} and dissipation work terms in the PZ, we are able to derive the size of the PZ.
We find that a description of the size of a theoretical PZ does not depend on the often-considered stiffness, which measures the relative stability between the convection zone and an adjacent radiative zone.

\subsection{Equations \& flux definitions}
\label{sec:theory_equations}
Throughout this work, we will utilize a modified version of the incompressible Boussinesq equations,
\begin{align}
&\grad\dot\vec{u} = 0 
\label{eqn:incompressible} \\
&\partial_t \vec{u} + \vec{u}\dot\grad\vec{u} = -\frac{1}{\rho_0}\grad p + \frac{\rho_1}{\rho_0}\vec{g} + \nu\grad^2 \vec{u} 
\label{eqn:momentum} \\
&\partial_t T + \vec{u}\dot\grad T + w \gradad + \grad\dot[-k \grad \overline{T}] = \chi\grad^2 T' + Q
\label{eqn:temperature} \\
&\frac{\rho_1}{\rho_0} = -|\alpha| T.
\label{eqn:boussinesq}
\end{align}
Here, the density is decomposed into a uniform, constant background $\rho_0$ with fluctuations $\rho_1$ which appear only in the buoyancy force and depend on the temperature $T$ and the coefficient of thermal expansion $\alpha = \partial\ln\rho / \partial T$.
We define the velocity vector $\vec{u}$, \editone{the pressure $p$,} the viscous diffusivity $\nu$, the thermal diffusivity $\chi$, the bulk internal heating $Q$, the adiabatic gradient $\gradad$, and a height-dependent thermal conductivity $k$.
We will consider Cartesian coordinates $(x, y, z)$ with a constant vertical gravity $\vec{g} = -g\hat{z}$.
Throughout this work, we will represent horizontal averages with bars ($\overline{\,\cdot\,}$) and fluctuations away from those averages with primes ($'$).
Thus, in Eqn.~\ref{eqn:temperature}, $\bar{T}$ is the horizontally averaged temperature and $T'$ are fluctuations away from that; both of these fields evolve in time according to Eqn.~\ref{eqn:temperature}.

@@

\begin{figure}[t!]
\centering
\includegraphics[width=\columnwidth]{theory_profiles.pdf}
\caption{
Temporally- and horizontally-averaged profiles from Eqn.~\ref{eqn:kinetic_energy_1D} in the simulation in Fig.~\ref{fig:vertical_dynamics_panels}.
The vertical dashed line denotes the Schwarzschild CZ boundary, and the vertical solid line corresponds to the top of the PZ.
(upper) Kinetic energy fluxes $\bar{\mathcal{F}_{\editone{z}}}$, which go to zero at the bottom boundary and the top of the PZ.
    (bottom) Source terms from Eqn.~\ref{eqn:kinetic_energy_1D} normalized by the maximum of $\overline{\mathcal{B}}$ ($\bar{\mathcal{F}_{\editone{z}}}$ in the upper panel is similarly normalized).
The buoyancy source $\bar{\mathcal{B}}$ changes sign at the Schwarzschild boundary, and $\bar{\Phi}$ is positive-definite.
\label{fig:theory_profiles}
}
\end{figure}

Taking a dot product of the velocity and Eqn.~\ref{eqn:momentum} reveals the kinetic energy equation,
\begin{equation}
\frac{\partial \mathcal{K}}{\partial t}
    + \grad\dot\editone{\vec{\mathcal{F}}}
= \mathcal{B} - \Phi,
%\frac{\partial}{\partial t}\left(\frac{|\vec{u}|^2}{2}\right) 
%+ \grad\dot\left[\vec{u}\left(\frac{|\vec{u}|^2}{2} + \frac{p}{\rho_0}\right) - \nu\vec{u}\cross\vec{\omega}\right]
%= |\alpha| g w T - \nu|\vec{\omega}|^2,
\label{eqn:kinetic_energy}
\end{equation}
where we define the kinetic energy $\mathcal{K} \equiv |\vec{u}|^2/2$, the fluxes of kinetic energy $\editone{\vec{\mathcal{F}}} \equiv \left[\vec{u}(\mathcal{K} + p/\rho_0) - \nu\vec{u}\cross\vec{\omega} \right]$, the buoyant energy generation rate $\mathcal{B} \equiv |\alpha| g w T'$, and the viscous dissipation rate $\Phi \equiv \nu |\vec{\omega}|^2$ where $\vec{\omega} = \grad\cross\vec{u}$ is the vorticity and $|\vec{u}|^2 = \vec{u}\dot\vec{u}$ \& $|\vec{\omega}|^2 = \vec{\omega}\dot\vec{\omega}$.
We next take a horizontal- and time-average of Eqn.~\ref{eqn:kinetic_energy} (we absorb the time-average into the horizontal-average $\bar{\,\cdot\,}$ notation for simplicity).
Assuming that $\bar{\mathcal{K}}$ reaches a statistically stationary state, convective motions satisfy
\begin{equation}
    \frac{d\bar{\mathcal{F}_{\editone{z}}}}{dz} = \bar{\mathcal{B}} - \bar{\Phi},
\label{eqn:kinetic_energy_1D}
\end{equation}
\editone{where $\mathcal{F}_z$ is the z-component of $\vec{\mathcal{F}}$.}
Each profile in Eqn.~\ref{eqn:kinetic_energy_1D} is shown in Fig.~\ref{fig:theory_profiles} for the simulation whose dynamics are displayed in Fig.~\ref{fig:vertical_dynamics_panels}.
As in Fig.~\ref{fig:grad_profiles}, the Schwarzschild CZ boundary is plotted as a dashed line, and the top of the PZ is plotted as a solid vertical line.
In the top panel, we display $\bar{\mathcal{F}_{\editone{z}}}$, neglecting the viscous flux term which is only nonzero in a small region above the bottom boundary.
We see that $\bar{\mathcal{F}_{\editone{z}}}$ is zero at the bottom boundary (left edge of plot) and at the top of the PZ.
In the bottom panel, we plot $\bar{\mathcal{B}}$ and $\bar{\Phi}$; we see that $\bar{\mathcal{B}}$ changes sign at the Schwarzschild CZ boundary, and that $\bar{\Phi}$ is positive-definite.

At the boundaries of the convecting region, $\bar{\mathcal{F}_{\editone{z}}}$ is zero (Fig.~\ref{fig:theory_profiles}, upper panel).
We integrate Eqn.~\ref{eqn:kinetic_energy_1D} vertically between these zeros to find
\begin{equation}
\int \bar{\mathcal{B}}\,dz = \int \bar{\Phi}\,dz.
\label{eqn:integral_constraint}
\end{equation}
Integral constraints of this form are the basis for a broad range of analyses in Boussinesq convection \citep[see e.g.,][]{ahlers_etal_2009, goluskin2016} and were considered in the context of penetrative stellar convection by \citet{roxburgh1989}.
Eqn.~\ref{eqn:integral_constraint} is the straightforward statement that work by buoyancy on large scales must be balanced by viscous dissipation on small scales.

We break up the convecting region into a Schwarzschild-unstable ``convection zone'' (CZ) and an extended ``penetration zone'' (PZ); we assume that convective motions efficiently mix $\justgrad \rightarrow \gradad$ in both the CZ and PZ.
The buoyant energy generation is proportional to the convective flux, $\bar{\mathcal{B}} = |\alpha|g\bar{w T'} = |\alpha| g \bar{\Fconv}$, and is positive in the CZ and negative in the PZ (see Fig.~\ref{fig:theory_profiles}, bottom panel).
Breaking up Eqn.~\ref{eqn:integral_constraint}, we see that
\begin{equation}
%\int_{\rm{CZ}} \bar{\mathcal{B}}\,dz \qquad=\qquad
\int_{\rm{CZ}} \bar{\mathcal{B}}\,dz \,\,=\,\,
\int_{\rm{CZ}} \bar{\Phi}\,dz + \int_{\rm{PZ}} \bar{\Phi}\,dz + \int_{\rm{PZ}}(-\bar{\mathcal{B}})\,dz.
\label{eqn:constraint_cz_pz_split}
\end{equation}
Eqn.~\ref{eqn:constraint_cz_pz_split} is arranged so that the (positive) buoyant engine of convection is on the left-hand side, and the (positive) sinks of work are on the RHS.
If viscous dissipation in the CZ does not balance the buoyant generation of energy in the CZ, the kinetic energy of the convective flows grows, resulting in a penetrative region.
This region grows with time until Eqn.~\ref{eqn:constraint_cz_pz_split} is satisfied.
We see that the viscous dissipation and \editone{buoyant deceleration} felt by flows in the PZ determine its size.
We now define
\begin{equation}
f \equiv \frac{\int_{\rm{CZ}} \bar{\Phi}\,dz}{\int_{\rm{CZ}}\bar{\mathcal{B}}\,dz},
\label{eqn:f_defn}
\end{equation}
the measurable fraction of the buoyant engine consumed by CZ dissipation.
Eqn.~\ref{eqn:constraint_cz_pz_split} can then be rewritten as
\begin{equation}
\frac{\int_{\rm{PZ}}(-\bar{\mathcal{B}})\,dz}{\int_{\rm{CZ}} \bar{\mathcal{B}}\,dz}
+ \frac{\int_{\rm{PZ}} \bar{\Phi}\,dz }{\int_{\rm{CZ}} \bar{\mathcal{B}}\,dz}
= (1 - f).
\label{eqn:first_pz_parameterization}
\end{equation}
We will measure and report the values of $f$ achieved in our simulations in this work.
Eqn.~\ref{eqn:first_pz_parameterization} provides two limits on a hypothetical PZ:
\begin{enumerate}
\item In the limit that $f \rightarrow 0$, viscous dissipation is inefficient.
Reasonably if we also assume that $\int_{\rm{PZ}}\bar{\Phi}\,dz \rightarrow 0$, Eqn.~\ref{eqn:first_pz_parameterization} states that the PZ must be so large that its negative buoyant work is equal in magnitude to the positive buoyant work of the CZ.
This is the integral constraint on the maximum size of the PZ that \citet{roxburgh1989} derived.
\item In the limit that $f \rightarrow 1$, viscous dissipation efficiently counteracts the buoyancy work in the CZ.
Per Eqn.~\ref{eqn:first_pz_parameterization}, the positive-definite PZ terms must approach zero and no PZ develops in this limit.
This is mathematically equivalent to standard boundary-driven convection experiments.
\end{enumerate}
In general, we anticipate from the results of e.g., \citet{currie_browning_2017} that $f$ is closer to 1 than 0, but its precise value must be measured from simulations.
Indeed, we find that $f \gg 0$ but $f < 1$ in our simulations (see e.g., Fig.~\ref{fig:theory_profiles}, bottom panel\footnote{the bulk dynamics suggest by eye $f \sim 0.5$, but due to e.g., the height dependence of $\bar{\mathcal{B}}$ in our simulations we measure $f \approx 0.74$.}).
Our simulations produce typical values of $f \sim 0.7$.

Assuming that a PZ of height $\delp$ develops above a CZ of depth $L_{\rm{CZ}}$, we model the PZ dissipation as
\begin{equation}
\int_{\rm{PZ}} \bar{\Phi}\,dz = \xi\frac{\delp}{L_{\rm{CZ}}}\int_{\rm{CZ}}\bar{\Phi}\,dz = \xi \delp \Phi_{\rm{CZ}}.
\label{eqn:xi_defn}
\end{equation}
Here $\Phi_{\rm{CZ}}$ is the volume-averaged dissipation rate in the CZ and $\xi$ is a measurable parameter in ${[0, 1]}$ that describes the shape of the dissipation profile as a function of height in the PZ.
In words, we assume that $\bar{\Phi}(z = L_s) \approx \Phi_{\rm{CZ}}$ at the CZ-PZ boundary and that $\bar{\Phi}$ decreases with height in the PZ.
The shape of $\bar{\Phi}$ determines $\xi$; a linear falloff gives $\xi = 1/2$, a quadratic falloff gives $\xi = 2/3$, and $\xi = 1$ assumes no falloff.
With this parameterization, and $\bar{\mathcal{B}} \propto \bar{\Fconv}$, we rewrite Eqn.~\ref{eqn:first_pz_parameterization},
\begin{equation}
-\frac{\int_{\rm{PZ}}\bar{\Fconv}\,dz}{\int_{\rm{CZ}}\bar{\Fconv}\,dz} + f\xi\frac{\delp}{L_{\rm{CZ}}}
= (1 - f).
\label{eqn:theory_fraction}
\end{equation}
The fundamental result of this theory is Eqn.~\ref{eqn:theory_fraction}, which is a parameterized and generalized form of \citet{roxburgh1989}'s integral constraint.
This equation is also reminiscent of \citet{zahn1991}'s theory, and says that the size of a PZ is set by the profile of $\gradrad$ near the convective boundary.
A parameterization like Eqn.~\ref{eqn:theory_fraction} can be implemented in stellar structure codes and used to find the extent of penetration zones under the specification of $f$ and $\xi$.
\editone{
    We note that an implementation of Eqn.~\ref{eqn:theory_fraction} likely requires an \emph{iterative} solve, as the penetration zone depth ($\delp$) and thus the PZ integral of the flux, are not known \emph{a-priori}.
}
The parameters $f$ and $\xi$ are measurables which can be constrained by direct numerical simulations, and we will measure their values in this work.
In general, we expect that $f$ and $\xi$ should not change too drastically with other simulation parameters.
